Response to Pachter’s Review

### 2020-01-22 index.Rmd
typo
minor bug addressed mean calc

We calculate the average citations/average year since PhD of letters A, B, and C, and compare them to our ranked list.

```{r, echo = FALSE, include = FALSE}
mean(filter(df, ((lettergroup == "A Only"|lettergroup == "A and B")&(role=="professor")&(field=="math")))$amscitperyear, na.rm = TRUE)

mean(filter(df, ((lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B")&(role=="professor")&(field=="math")))$amscitperyear, na.rm = TRUE)

mean(filter(df, ((lettergroup == "C Only"|lettergroup == "B and C")&(role=="professor")&(field=="math")))$amscitperyear, na.rm = TRUE)
```

@@

2. For letter B - 41.86467

3. For letter C - 55.3615

>>>>

We calculate the average citations per year since PhD of letters A, B, and C, and compare them to our ranked list.

```{r, echo = FALSE, include = FALSE}
mean(filter(df, (lettergroup == "A Only"|lettergroup == "A and B"))$amscitperyear, na.rm = TRUE)
mean(filter(df, (lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B"))$amscitperyear, na.rm = TRUE)
mean(filter(df, (lettergroup == "C Only"|lettergroup == "B and C"))$amscitperyear, na.rm = TRUE)
```

@@

2. For letter B - 41.12345

3. For letter C - 55.5451
